### 2020-09-05 text/manuscript.tex
Fix suggestions of Gergely. This is consistent with 10.5281/zenodo.4016325

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Retail, accommodation and restaurants are the most communication intensive.}}
\begin{tabular}{|l+c|c|c+c|}
\hline
 & \multicolumn{3}{c}{\bf Communication} &  
\\ 
{\bf Industry} & {\bf Teamw.} & {\bf Custom.} & {\bf Overall} & {\bf Presence} 
\\ \thickhline
Retail trade 						&13	&66	&67	&5\\
Accommodation \& food services 		&8	&50	&51	&1\\
Arts, Entertainment, and Recreation &12	&38	&40	&2\\
Other Services (except Public Admin.)&12&30	&33	&12\\
Admin. \& Support \& Waste Manag.  	&17	&24	&27	&7\\
...&&&&\\
Wholesale Trade						&8	&12	&15	&12\\
Transportation and Warehousing 		&8	&8	&14	&33\\
Prof., Scient., and Technical Serv.	&5	&10	&12	&1\\
Manufacturing 						&7	&5	&9	&10\\
Agri., forestry, fishing \& hunting &4	&1	&4	&23\\

@@

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf The five most affected sectors require more than 14 percent wage subsidy.}}
\begin{tabular}{|l+c|c|}
\hline
{\bf Industry} & {\bf Wage subsidy} & {\bf Employment} 
\\ \thickhline
Retail Trade	&234	&15,672\\
Arts, Entertainment, and Recreation	&30.2	&2,472\\
Accommodation and Food Services	&26.1	&14,394\\
Educational Services	&22.2	&3,8328\\
Other Services (except Public Admin.)	&14.5	&5,941\\
...&&\\
Wholesale Trade	&1.8	&5,934\\
Construction	&1.1	&7,639\\
Manufacturing	&1.1	&12,852\\
Management of Companies and Enterprises	&1.1	&2,447\\
Agriculture, Forestry, Fishing and Hunting	&0.5	&55\\
\hline
{\bf Average} & {\bf 39.9} & {\bf 116,441}\\
 \thickhline

>>>>

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Retail, accommodation and restaurants are the most communication intensive.}}
\begin{tabular}{|l+c|c|c+c|}
\hline
 & \multicolumn{3}{c}{\bf Communication} &  
\\ 
{\bf Industry} & {\bf Teamw.} & {\bf Custom.} & {\bf Overall} & {\bf Presence} 
\\ \thickhline
Retail trade 						&13	&66	&67	&5\\
Accommodation \& food services 		&8	&50	&51	&1\\
Arts, Entertainment, and Recreation &12	&38	&40	&2\\
Other Services (except Public Admin.)&12&30	&33	&12\\
Admin. \& Support \& Waste Manag.  	&17	&24	&27	&7\\
...&&&&\\
Wholesale Trade						&8	&12	&15	&12\\
Transportation and Warehousing 		&8	&8	&14	&32\\
Prof., Scient., and Technical Serv.	&5	&10	&12	&1\\
Manufacturing 						&7	&5	&9	&10\\
Agri., forestry, fishing \& hunting &4	&1	&4	&23\\

@@

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf The five most affected sectors require more than 14 percent wage subsidy.}}
\begin{tabular}{|l+c|c|}
\hline
{\bf Industry} & {\bf Wage subsidy} & {\bf Employment} 
\\ \thickhline
Retail Trade	&234	&15,672\\
Arts, Entertainment, and Recreation	&30.2	&2,472\\
Accommodation and Food Services	&26.1	&14,394\\
Educational Services	&22.2	&3,828\\
Other Services (except Public Admin.)	&14.5	&5,941\\
...&&\\
Wholesale Trade	&1.8	&5,934\\
Construction	&1.1	&7,639\\
Manufacturing	&1.1	&12,852\\
Management of Companies and Enterprises	&1.1	&2,447\\
Agriculture, Forestry, Fishing and Hunting	&0.5	&55\\
\hline
{\bf Average} & {\bf 39.9} & {\bf 116,441}\\
 \thickhline
